\documentclass[../../main]{subfiles}
\begin{document}

In this section it is concluded to what extend the problems in the problem statements is solved.

\paragraph{Control engineering}

A mathematical model of the pan-tilt system has been made. \todo{It is noticed that in this model, both the top and bottom frame are nonlinear.}

A nonlinaerity is here observed for the top and bottom frame.
The top frame's nonlinaerity is approximated by linearization with the Jacobian matrix in angles $0^\circ$, $90^\circ$ and $180^\circ$.
\todo{The top frame is therefore linearized in the angles $0^\circ$, $90^\circ$ and $180^\circ$ by calculating the Jacobian matrix. }
\todo{As for the bottom frame's non-linearity, it is shown that the influence caused by the position of the top frame is negligible. This is shown by a step response, in which the top frame is set to the aforementioned angles.}
It is  here determined that the bottom frame is dependent on the top frame, but the top frames effect is negligible.



Based on the modelled system, \todo{a PI-controller has been tuned with the gains $K_p$ and $T_i$. It has then further been tuned by hand, in order to achieve the performance specifications to the best extend possible. } a PI-controller has be with $K_p$ and $T_i$ gains have been tuned and then tuned by hand to comply with the performance specifications to the best extend possible.

\todo{The PI-controller has been implemented on the tiva, by deriving the difference equation using Tustin's method. }
This controller is implemented on the using tustin's method Tiva.
\todo{Futhermore step responses of the acutal system have been logged. (This is in order to achieve a comparison of the ...)  This is to compare the physical and mathematical systems. }
Step responses of the actual system have been logged and compared with the expected step responses from the mathematical model.
\todo{In the comparison it is seen that, the mathematical model have almost no overshoot, opposed to the actual system which capable of reaching an overshoot of 38\% }
The step responses based on the mathematical model have no overshoot compared with the actual system.

\todo{Since the step responses are too dissimilar, it is concluded that the model itself is too inaccurate to be applied directly as a tool to tune the system.   }
Based on the results it is concluded that the mathematical model is not accurate enough to apply directly.\\

\paragraph{Digital System Design}
On the FPGA, decoders are implemented in order to measure the positon of the system.
This is achieved by decoding the signals from the quadrature encoders of the pan-tilt system.

The FPGA can determine the position with a \todo{The resolution of the position and direction measurement is  } $\frac{1}{3}$ degrees of precision, and direction, in which the system is rotating.
\todo{Based on the quadrature decoder, a unit on the FPGA for measuring the velocity has been implemented. }
A velocity has been implemented, which can be calculated from the position.\\

\todo{Futhermore the FPGA acts as the motor controller, this is achieved by an implementing a PWM module.}

. This is done with a implemented PWM module.\\

The PWM signal's frequency has been calculated to be $1003 \si{\,Hz}$, as this allows the motor to draw full current and utilize all available torque. \\
\todo{as this allow for the motor to draw full current, and therefore utilize its potential torque.}

The SPI protocol is a shift register protocol with a register size varying from \todo{ from 8 to 16 bits} 8 bits to a maximum of 16 bits.
The protocol follows the master/slave principle, in which the Tiva acts as the master and the FPGA as slave. This protocol has been implemented on the FPGA by using a SPI module.

\paragraph{Embedded Programming}
A real time operating system, FreeRTOS, has been implemented on the Tiva. FreeRTOS has been chosen \todo{as this provides a scheduler, and thus making multiple task run in parallel possible.} as it can  emulate tasks running in parallel. \\
The controllers are implemented on the Tiva as tasks having the highest priority. This is to ensure the timings are consistent.

\begin{itemize}
  \item PI controller choice
  \item control engineering:
  \begin{itemize}
    \item issue with nonlinaer modeling - how did we solve this?
    \item top and bottom frrame - two "individual" systems - are. theoretically fulfilling our requirements
    \item reality vs theoretical top and bottom frame - plus the finished handtuned values for Ki and Kp
  \end{itemize}
  \item design choices FPGA:
    \begin{itemize}
      \item Encoder - position counting with 1080 ticks or 1/3 degrees precision
      \item SPI - Protocol used
      \item PWM
      \item Homing?
    \end{itemize}
  \item embedded:
  \begin{itemize}
    \item Pi micrcontroller
    \item FreeRTOS
  \end{itemize}


\end{itemize}


\end{document}
